--- 
title: "UCB Data Dictionary"
author: "Ben Croft"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This book is a prototype of a functional Data Dictionary for University of Colorado Boulder."
---

# Overview

This book is a prototype of a functional **Data Dictionary**. 

As a proof of concept, the book serves as a demonstration of what University of Colorado Boulder may adopt as _open, collaborative, and living documentation_ of data, data sets, and data applications. This proof of concept is version-controlled with Git, which enables version history, cross-team development, and rapid development. Additionally, this book can be hosted within Github Pages for public - or private - sharing among the campus system. Finally, this book can also be downloaded as a PDF, Ebook, or LaTeX file using the buttons at the top of this page. 

Since this data dictionary is written in Markdown, it can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

